abxD01 Paper

### 2015-04-09 Schubert_abxD01_mBio_2015.Rmd
Add Table 1 to manuscript

>>>>

Table 1. Description of Antibiotics used in this study

Antibiotic | Administration | Class | Mechanism | Target
:---------:|:--------------:|:-----:|:---------:|:---------:
Ciprofloxacin | Oral gavage, one time | Fluoroquinolone | Inhibits DNA gyrase | Gram +/-
Clindamycin | IP injection, one time | Lincosamide | Inhibits protein synthesis | Anaerobes
Vancomycin | *Ad libitum* in drinking water, five days | Glycopeptide | Inhibits peptidoglycan synthesis | Gram +
Streptomycin | *Ad libitum* in drinking water, five days | Aminoglycoside | Inhibits protein synthesis | Gram +/-
Cefoperazone | *Ad libitum* in drinking water, five days | β-lactam: Cephalosporin | Inhibits peptidoglycan synthesis | Gram +/-
Ampicillin | *Ad libitum* in drinking water, five days | β-lactam: Penicillin | Inhibits peptidoglycan synthesis | Gram +/-
Metronidazole | *Ad libitum* in drinking water, five days | Nitromidazole | Destabilizes bacterial DNA | Anaerobes
